### 2019-10-14 ch3_dynbenchmark/content.tex
fix minor issues

We gathered a list of 71 trajectory inference tools (Supplementary Table 1) by searching the literature for ‘trajectory inference’ and ‘pseudotemporal ordering’, and based on two existing lists found online: \href{https://github.com/seandavi/awesome-single-cell}{https://github.com/seandavi/awesome-single-cell} \cite{davis_awesomesinglecell_2018} and \href{https://github.com/agitter/single-cell-pseudotime}{https://github.com/agitter/single-cell-pseudotime} \cite{gitter_singlecellrnaseqpseudotime_2018}. We welcome any contributions by creating an issue at https://methods.dynverse.org.

@@

* Linear and cyclic, with number of milestones $\sim B(10, 0.25)$
* Bifurcating and converging, with four milestones
* Binary tree, with number of branching points $\sim U(3, 6)$
* Tree, with number of branching points $\sim U(3, 6)$ and maximal degree $\sim U(3, 6)$

@@

* Looping, allowed loop modifications
* Diverging-converging, allowed divergence and converging modifications
* Diverging with loops, allowed divergence and loop modifications
* Multiple looping, allowed looping modifications
* Connected, allowed looping, divergence and convergence modifications
* Disconnected, number of components sampled from $\sim B(5, 0.25) + 2$, for each component we randomly chose a topology from the ones listed above

>>>>

We gathered a list of 71 trajectory inference tools (Supplementary Table 1) by searching the literature for ‘trajectory inference’ and ‘pseudotemporal ordering’, and based on two existing lists found online: \href{https://github.com/seandavi/awesome-single-cell}{awesome-single-cell} \cite{davis_awesomesinglecell_2018} and \href{https://github.com/agitter/single-cell-pseudotime}{single-cell-pseudotime} \cite{gitter_singlecellrnaseqpseudotime_2018}. We welcome any contributions by creating an issue at \href{https://methods.dynverse.org}{https://methods.dynverse.org}.

@@

\begin{itemize}
	\item Linear and cyclic, with number of milestones $\sim B(10, 0.25)$
	\item Bifurcating and converging, with four milestones
	\item Binary tree, with number of branching points $\sim U(3, 6)$
	\item Tree, with number of branching points $\sim U(3, 6)$ and maximal degree $\sim U(3, 6)$
\end{itemize}

@@

\begin{itemize}
	\item Looping, allowed loop modifications
	\item Diverging-converging, allowed divergence and converging modifications
	\item Diverging with loops, allowed divergence and loop modifications
	\item Multiple looping, allowed looping modifications
	\item Connected, allowed looping, divergence and convergence modifications
	\item Disconnected, number of components sampled from $\sim B(5, 0.25) + 2$, for each component we randomly chose a topology from the ones listed above
\end{itemize}
